### 2022-05-31 main/chapter_2ljets.tex
add top q observation example

>>>>

Events appearing in a region with minimal background is evidence in favour
of new contributions, and that only strengthens as the background approaches
zero.
For example, the top quark was observed by D0 in 1995 using seven regions all with
background expectations of $1$ or less~\cite{abachi1995observation},
for a total of $3.79\pm0.55$ expected and $17$ observed.
If they could do that with 20th century technology, we can do it now.
